Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.6)} \underline{Drafting Committee: DC90 (\today)}

### 2011-02-11 background_and_systematic.tex
Penultimate reading of the paper before circulation to the drafting committee. Fixed a few typos, re-flowed a couple of sentences to improve coherency with previous changes. Swapped a couple of the references around.

\section{Background Corrections and Systematic Uncertainties}
The extracted asymmetry amplitudes are subject to systematic uncertainties that
result from a combination of background processes, year-dependent
shifts in the missing-mass event distributions and various detector and binning
effects determined as in Ref\blue{s}.~\cite{Air08,Air09}. The
\blue{1996-2005} data sample also has a systematic uncertainty from misalignment of the spectrometer\blue{, which} was eliminated for the 2006-2007 data sample. Contributions to the uncertainties on the amplitude measurements arise from \blue{background in the data from} events that include neutral meson production. The procedure is described in detail in Refs.~\cite{Air08,Air09} and the contributions to the uncertainties of the measurements addressed here are given in Table~\ref{table_systematic_contributions_0607}. The largest \blue{contamination in} the data sample is expected to come from the \blue{excitation of a target proton to a $\Delta^+$ resonance. The separation of these events from the elastic sample is not feasible because the recoiling proton is not detected. No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal}. A Monte Carlo calculation based on the parameterisation of Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin. The results, denoted associated fraction and labelled ``assoc. fraction'', are shown in the last row of each figure in the results section. The method used to perform the estimation is described in detail in
Ref.~\cite{Air08}.

@@

The predominant contribution to the systematic uncertainty arises from detector
effects, including the acceptance of the spectrometer, smearing effects \blue{due to detector resolution and radiative processes}, and
finite bin width in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. In order to quantify
these effects, DVCS/BH events were generated using a Monte Carlo simulation of
the spectrometer that included these effects. The simulation used an event
generator based on the GPD model described in Ref.~\cite{Guz06} because it describes the data well and to keep consistency with Ref.~\cite{Air09}. Asymmetry amplitudes were extracted from these simulated events using the same analysis
procedure used to extract amplitudes from experimental data.  In each kinematic
bin, the systematic uncertainty was determined as the difference between the
asymmetry amplitude reconstructed from the simulated DVCS/BH data and that
calculated from the same GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.
The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin from the uncertainty contributions of the
background corrections, detector effects and missing-mass shift
uncertainties added in quadrature. These contributions are \blue{summarised} in Table
\ref{table_systematic_contributions_0607}.

>>>>

\section{Background Corrections and Systematic Uncertainties}
The extracted asymmetry amplitudes are subject to systematic uncertainties that
result from a combination of background processes, 
shifts in the missing-mass event distributions and various detector and binning
effects determined as in Ref\blue{s}.~\cite{Air08,Air09}. The
\blue{1996-2005} data sample also has a systematic uncertainty from misalignment of the spectrometer\blue{, which has been} eliminated for the 2006-2007 data sample. Contributions to the uncertainties on the amplitude measurements arise from \blue{background in the data from} events that include neutral meson production. The procedure is described in detail in Refs.~\cite{Air08,Air09} and the contributions to the uncertainties of the measurements addressed here are given in Table~\ref{table_systematic_contributions_0607}. The largest \blue{contamination in} the data sample is expected to come from the \blue{events involving the excitation of a target proton to a $\Delta^+$ resonance. The separation of these events from the elastic sample is not feasible because the recoiling proton is not detected. No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal}. A Monte Carlo calculation based on the parameterisation of Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin. The results, denoted associated fraction and labelled ``assoc. fraction'', are shown in the last row of each figure in the results section. The method used to perform the estimation is described in detail in
Ref.~\cite{Air08}.

@@

The predominant contribution to the systematic uncertainty arises from detector
effects, including the acceptance of the spectrometer, smearing effects \blue{due to detector resolution and radiative processes}, and
finite bin width in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. In order to quantify
these effects, DVCS/BH events were generated using a Monte Carlo simulation of
the spectrometer that included \blue{them}. The simulation used an event
generator based on the GPD model described in Ref.~\cite{Guz06} because it describes the data well and to keep consistency with Ref.~\cite{Air09}. Asymmetry amplitudes were extracted from these simulated events using the same analysis
procedure used to extract amplitudes from experimental data.  In each kinematic
bin, the systematic uncertainty was determined as the difference between the
asymmetry amplitude reconstructed from the simulated DVCS/BH data and that
calculated from the same GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.
The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin from the uncertainty contributions of the
background corrections, detector effects and missing-mass shift
uncertainties added in quadrature. These contributions are \blue{summarised} in Table
\ref{table_systematic_contributions_0607}.

### 2011-02-11 experiment_and_data.tex
Penultimate reading of the paper before circulation to the drafting committee. Fixed a few typos, re-flowed a couple of sentences to improve coherency with previous changes. Swapped a couple of the references around.

\section{Experiment and Data Selection}
The data were collected in 2006 and 2007 with the H{\sc ermes}
spectrometer \cite{Ack98} using the longitudinally polarised 27.6\,GeV
electron and positron beams incident upon an unpolarised hydrogen gas
target internal to the HERA lepton storage ring at DESY. The integrated
luminosities of the electron and positron data samples respectively are
approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$\blue{,} with average beam polarisation\blue{s} of 30.3\,\% and 39.2\% \cite{Ben01}. The procedure used to select events is identical to that used in Ref.~\cite{Air09}.
A brief summary of this procedure is outlined in the following; consult
Refs.~\cite{Zei09,Bur10} for more details. An event
was selected as having exactly one photon and one lepton
track detected within the acceptance of the spectrometer.

@@

The asymmetry amplitudes $A_{\textrm{LU,I/DVCS}}^{\sin(n\phi)}$ and
$A_{\textrm{C}}^{\cos(n\phi)}$ relate respectively to the Fourier
coefficients $s_{n}^{W}$ and $c_{n}^{V}$ from the interference and DVCS terms in Eqs.~\ref{e:alui}-\ref{e:ac}. The asymmetry amplitudes may also be affected by the lepton progopagators and the other $\phi$-dependent terms in the denominators in Eqs.~\ref{e:alui}-\ref{e:ac}. The  $s_{n}^{W}$ and $c_{n}^{V}$ Fourier coefficients are \blue{depend on}  ``$\mathcal{C}$-functions''\blue{,} each \blue{of which} $\mathcal{C}$-function is a combination of complex Compton Form Factors. \blue{A CFF is a convolution of a GPD with a hard scattering kernel}. \blue{Contributions of GPDs to the cross section may ne relatively suppressed by powers of $1/Q$, the origin of which may be kinematic in nature or due to the twist level of the GPD.} The access from each asymmetry amplitude to a GPD is called twist-$n$ depending upon the part of the twist-decomposed cross-section in which the amplitude appears. Leading twist is twist-2. Typically, the contribution of a \blue{twist-$n$} GPD, and hence the corresponding CFF, is suppressed by $\mathcal{O}(1/Q^{n-2})$. \blue{Table~\ref{tab_amplitudes} presents t}he asymmetry amplitudes extracted in this analysis and the related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and levels of suppression\blue{.}

At H{\sc ermes} kinematic\blue{ conditions}, the leading-twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$. These asymmetry amplitudes for an unpolarised target are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$. Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
\begin{center}
\begin{equation}
 s_{1,\textrm{unp}}^{\textrm{I}} \approx 8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
\label{eq:s1}
\end{equation}
\end{center}
\begin{center}
\begin{equation}
 c_{1,\textrm{unp}}^{\textrm{I}} \approx 8k(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
\label{eq:c1}
\end{equation}
\end{center}
where the kinematic factor $k \propto \sqrt{-t}/Q$ originates from the BH
propagators. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
written
\cite{Bel02b} 
\begin{equation}
 \mathcal{C}_{\textrm{unp}}^{\textrm{I}} = F_{1}\mathcal{H} + \frac{x_{\textrm{B}}}{2-x_{\textrm{B}}}(F_{1}+F_{2})\widetilde{\mathcal{H}} -\frac{t}{4M^{2}}F_{2}\mathcal{E},
\label{Eq_cunp}
\end{equation}
where $F_{1}$ and $F_{2}$ are respectively the Dirac and Pauli form
factors of the nucleon and $\mathcal{H}$, $\widetilde{\mathcal{H}}$ and
$\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
$\widetilde{H}$ and $E$.  At H{\sc ermes} kinematic
conditions (where $x_{\textrm{B}}$ and $\frac{t}{4M^2}$ are of order 0.1), \blue{to first approximation} the
contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
neglected in Eq.~\ref{Eq_cunp} with respect to $\mathcal{H}$ since they
are kinematically suppressed by an order of magnitude or more.
Hence, \blue{in this} approximation, the behaviour of
$\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
and therefore GPD $H$. Using this dependence, $H$ can be constrained through
measurements of $A_{\textrm{LU,I}}^{\sin\phi}$ and $A^{\cos\phi}_{\textrm{C}}$.
The asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$,
$A^{\cos(0\phi)}_{\textrm{C}}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ also depend
upon this $\mathcal{C}$-function. However, the $A^{\cos(0\phi)}_{\textrm{C}}$ \blue{amplitude} is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, whereas the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ \blue{amplitudes} enter the cross section at a higher
twist level (see Table~\ref{tab_amplitudes}).

@@

The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
$c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ function. This
$\mathcal{C}$-function receives contributions from both the BH and DVCS
processes and therefore depends on $F_{1}$, $F_{2}$ and CFFs. Although the CFFs
in this function are \blue{of} leading twist, they relate to gluon helicity\blue{-}flip GPDs and are \blue{thus} suppressed by \blue{$\alpha_{\textrm{S}}/\pi$}.
\begin{table}[H]
\begin{center}
\resizebox{16cm}{!} {
 \begin{tabular}{|c|c|c|c|c|}
\hline
Asymmetry Amplitude & Fourier Coefficient& Dominant CFF Dependence & Twist Level  & Suppression \\
\hline
\hline
$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  2 & $n$ = 2\\
\hline
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{2,\textrm{unp}}^{\textrm{I}}$ 
&
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  3 & $n$ = 3\\
\hline
\hline
$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3& $n$
= 3 \\
\hline
\hline
$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& $n$ = 2
\\
\hline
$A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2 & $n$ = 2
\\
\hline
$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 & $n$ = 3 \\
\hline
$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 & $n$ = 2, $\alpha_{\textrm{S}}/\pi$ \\
\hline
 \end{tabular}
}
\caption{Asymmetry amplitudes that can
be extracted from the available data set, the related Fourier coefficients,
 the $\mathcal{C}$-functions, the twist level and the suppression \blue{at H{\sc ermes} kinematic conditions}~\cite{Bel02b}.}
\label{tab_amplitudes}
\end{center}
\end{table}

>>>>

\section{Experiment and Data Selection}
The data were collected in 2006 and 2007 with the H{\sc ermes}
spectrometer \cite{Ack98} using the longitudinally polarised 27.6\,GeV
electron and positron beams incident upon an unpolarised hydrogen gas
target internal to the HERA lepton storage ring at DESY. The integrated
luminosities of the electron and positron data samples respectively are
approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$\blue{,} with average beam polarisation\blue{s} of 30.3\,\% and 39.2\% \cite{Ben01}. The procedure used to select events is \blue{similar} to that used in Ref.~\cite{Air09}.
A brief summary of this procedure is outlined in the following; consult
Refs.~\cite{Zei09,Bur10} for more details. An event
was selected as having exactly one photon and one lepton
track detected within the acceptance of the spectrometer.

@@

The asymmetry amplitudes $A_{\textrm{LU,I/DVCS}}^{\sin(n\phi)}$ and
$A_{\textrm{C}}^{\cos(n\phi)}$ relate respectively to the Fourier
coefficients $s_{n}^{W}$ and $c_{n}^{V}$ from the interference and DVCS terms in Eqs.~\ref{e:alui}-\ref{e:ac}. The asymmetry amplitudes may also be affected by the lepton progopagators and the other $\phi$-dependent terms in the denominators in Eqs.~\ref{e:alui}-\ref{e:ac}. The  $s_{n}^{W}$ and $c_{n}^{V}$ Fourier coefficients \blue{depend on}  ``$\mathcal{C}$-functions''\blue{,} each \blue{of which} is a combination of complex Compton Form Factors. \blue{A CFF is a convolution of a GPD with a hard scattering kernel}. \blue{Contributions of GPDs to the cross section may be relatively suppressed by powers of $1/Q$, the origin of which may be kinematic in nature or due to the twist level of the GPD.} The access from each asymmetry amplitude to a GPD is called twist-$n$ depending upon the part of the twist-decomposed cross-section in which the amplitude appears. Leading twist is twist-2. Typically, the contribution of a \blue{twist-$n$} GPD, and hence the corresponding CFF, is suppressed by $\mathcal{O}(1/Q^{n-2})$. \blue{Table~\ref{tab_amplitudes} presents t}he asymmetry amplitudes extracted in this analysis and the related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and levels of suppression\blue{.}

At H{\sc ermes} kinematic\blue{ conditions}, the leading-twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$. These asymmetry amplitudes for an unpolarised target are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$. Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
\begin{center}
\begin{equation}
 s_{1,\textrm{unp}}^{\textrm{I}} \approx 8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
\label{eq:s1}
\end{equation}
\end{center}
\begin{center}
\begin{equation}
 c_{1,\textrm{unp}}^{\textrm{I}} \approx 8k(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
\label{eq:c1}
\end{equation}
\end{center}
where the kinematic factor $k \propto \sqrt{-t}/Q$ originates from the BH
propagators. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
written
\cite{Bel02b} 
\begin{equation}
 \mathcal{C}_{\textrm{unp}}^{\textrm{I}} = F_{1}\mathcal{H} + \frac{x_{\textrm{B}}}{2-x_{\textrm{B}}}(F_{1}+F_{2})\widetilde{\mathcal{H}} -\frac{t}{4M^{2}}F_{2}\mathcal{E},
\label{Eq_cunp}
\end{equation}
where $F_{1}$ and $F_{2}$ are respectively the Dirac and Pauli form
factors of the nucleon and $\mathcal{H}$, $\widetilde{\mathcal{H}}$ and
$\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
$\widetilde{H}$ and $E$.  At H{\sc ermes} kinematic
conditions (where $x_{\textrm{B}}$ and $\frac{t}{4M^2}$ are of order 0.1), \blue{to first approximation} the
contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
neglected in Eq.~\ref{Eq_cunp} with respect to $\mathcal{H}$ since they
are kinematically suppressed by an order of magnitude or more.
Hence, \blue{in this} approximation, the behaviour of
$\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
and therefore GPD $H$. Using this dependence, $H$ can be constrained through
measurements of $A_{\textrm{LU,I}}^{\sin\phi}$ and $A^{\cos\phi}_{\textrm{C}}$.
The asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$,
$A^{\cos(0\phi)}_{\textrm{C}}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ also depend
upon this $\mathcal{C}$-function. However, the $A^{\cos(0\phi)}_{\textrm{C}}$ \blue{amplitude} is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, \blue{and} the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ \blue{amplitudes} enter the cross section at a higher
twist level (see Table~\ref{tab_amplitudes}).

@@

The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
$c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ function. This
$\mathcal{C}$-function receives contributions from both the BH and DVCS
processes and therefore depends on $F_{1}$, $F_{2}$ and CFFs. Although the CFFs
in this function are \blue{of} leading twist, they relate to gluon helicity\blue{-}flip GPDs and are \blue{thus} suppressed by \blue{$\alpha_{\textrm{S}}/\pi$}.
\begin{table}[H]
\begin{center}
\resizebox{16cm}{!} {
 \begin{tabular}{|c|c|c|c|c|}
\hline
Asymmetry Amplitude & Fourier Coefficient& Dominant CFF Dependence & Twist Level  & \blue{Relative} Suppression \\
\hline
\hline
$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  2 & --\\
\hline
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{2,\textrm{unp}}^{\textrm{I}}$ 
&
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  3 & $1/Q$\\
\hline
\hline
$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3 & $1/Q$ \\
\hline
\hline
$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& --
\\
\hline
$A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2 & --
\\
\hline
$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 & $1/Q$ \\
\hline
$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 & $\alpha_{\textrm{S}}/\pi$ \\
\hline
 \end{tabular}
}
\caption{Asymmetry amplitudes that can
be extracted from the available data set, the related Fourier coefficients,
 the $\mathcal{C}$-functions, the twist level and the suppression \blue{at H{\sc ermes} kinematic conditions}~\cite{Bel02b}.}
\label{tab_amplitudes}
\end{center}
\end{table}

### 2011-02-11 results.tex
Penultimate reading of the paper before circulation to the drafting committee. Fixed a few typos, re-flowed a couple of sentences to improve coherency with previous changes. Swapped a couple of the references around.

\section{Results}
\blue{R}esults \blue{for} the beam-helicity and beam-charge asymmetry \blue{amplitudes} extracted separately from previously published 1996-2005~\cite{Air09} and the new 2006-2007 hydrogen data sets, are presented in Figs. \ref{release_bsa_0607} and \ref{release_bca_0607}. The asymmetry amplitudes extracted from the combined 1996-2007 hydrogen data set are shown in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange}. Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$. All of the extracted asymmetry amplitudes \blue{are subject to} a \blue{fractional} contribution to the event yield from associated \blue{production (``Assoc. fraction''), which} is shown in the bottom row of each figure. The beam-helicity asymmetry amplitudes are subject to an additional scale uncertainty from the measurement of the beam polarisation, which is stated in the captions of the figures.
\begin{figure}
\begin{center}
\includegraphics[width=15cm,keepaspectratio]{bsadvcsplots_eml_par13_bin6_release_pic_update_0607_9605}
  \caption{Beam-helicity asymmetry amplitudes extracted separately from
the 1996-2005 (open triangles) and 2006-2007 (filled squares)
hydrogen data.   
An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
2006-2007 data respectively is present in the amplitudes due to the \blue{im}precision of
the beam polarisation measurement. The inner error bars represent the statistical uncertainties\blue{, while} total error bars denote the statistical and systematic uncertainties added in quadrature. The \blue{simulated fractional} contribution \blue{from associated production} to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bsa_0607}
\end{center}
 \end{figure}
A \blue{statistical test was applied in order to check for possible incompatiability between the asymmetry amplitudes extracted from both data sets. Only the statistical uncertainties were employed in this test. The results} show that the \blue{the two} data sets are \blue{not incompatible}. The $A_{\textrm{LU,I}}$, $A_{\textrm{LU,DVCS}}$ and $A_{\textrm{C}}$ asymmetry amplitudes can therefore be extracted from the complete hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
\begin{figure}
\begin{center}
 \includegraphics[width=15cm,keepaspectratio]{bcaplots_eml_par13_bin6_release_pic_update_0607_9605_withassoc}
  \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles) and 2006-2007 (filled squares) hydrogen data.
The inner error bars represent the statistical uncertainties\blue{, while t}he total error bars denote the statistical and systematic uncertainties added in quadrature. The \blue{simulated fractional} contribution \blue{from associated production} to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bca_0607}
\end{center}
 \end{figure}

@@

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}. The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest value of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude has no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must diminish at low $t$ values due to the dependence of the amplitude on the factor $k$ from in Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The twist-3 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitudes are compatible with zero, as are the twist-3 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitudes dependent on the squared DVCS term. These are shown in the second row of Fig.~\ref{bsa_xbjrange}. Neither of these amplitudes show any clear dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$. The systematic error bands of the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used \blue{used in the various stages} of the H{\sc ermes} experiment.

@@

The curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data\cite{Kum09}. The basic model is based on a minimalist dual representation of GPDs with only (very) weakly entangled skewedness and $t$ dependences. In the model, the $t$ dependence is approximated by a physically-motivated Regge dependence. The solid curves represent the model \blue{fit} without data from the experiment \cite{Gir08,Cam06} at Hall A in Jefferson Laboratory; the model \blue{fit} represented by the dashed curves incorporates this data in the fit for an extraction of the GPDs. Both fits include the 1996-2005 H{\sc ermes} data. The model incorporates only twist-2 GPDs and so can provide calculations only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is well described by the model. \blue{Both the $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes favour the GPD fit that did not include the Hall A data.}

The asymmetry amplitudes shown in Figs.~\ref{release_bsa_0607} and \ref{release_bca_0607} were also re-binned as a function of $-t$ for three different ranges of $x_{\textrm{B}}$. There was no observed dependence of any of the amplitudes with this two dimensional binning.

>>>>

\section{Results}
\blue{R}esults \blue{for} the beam-helicity and beam-charge asymmetry \blue{amplitudes} extracted separately from previously published 1996-2005 and the new 2006-2007 hydrogen data sets, are presented in Figs. \ref{release_bsa_0607} and \ref{release_bca_0607}. Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$. All of the extracted asymmetry amplitudes \blue{are subject to} a \blue{fractional} contribution to the event yield from associated \blue{production (``Assoc. fraction''), which} is shown in the bottom row of each figure. The beam-helicity asymmetry amplitudes are subject to an additional scale uncertainty from the measurement of the beam polarisation, which is stated in the captions of the figures.
\begin{figure}
\begin{center}
\includegraphics[width=15cm,keepaspectratio]{bsadvcsplots_eml_par13_bin6_release_pic_update_0607_9605}
  \caption{Beam-helicity asymmetry amplitudes extracted separately from
the 1996-2005 (open triangles) and 2006-2007 (filled squares)
hydrogen data.   
An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
2006-2007 data respectively is present in the amplitudes due to the \blue{im}precision of
the beam polarisation measurement. The inner error bars represent the statistical uncertainties\blue{, while} total error bars denote the statistical and systematic uncertainties added in quadrature. The \blue{simulated fractional} contribution \blue{from associated production} to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bsa_0607}
\end{center}
 \end{figure}

A \blue{statistical test was applied in order to check for possible incompatiability between the asymmetry amplitudes extracted from both data sets. Only the statistical uncertainties were employed in this test. The results} show that the \blue{the two} data sets are \blue{not incompatible}. The $A_{\textrm{LU,I}}$, $A_{\textrm{LU,DVCS}}$ and $A_{\textrm{C}}$ asymmetry amplitudes can therefore be extracted from the complete hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
\begin{figure}
\begin{center}
 \includegraphics[width=15cm,keepaspectratio]{bcaplots_eml_par13_bin6_release_pic_update_0607_9605_withassoc}
  \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles) and 2006-2007 (filled squares) hydrogen data.
The inner error bars represent the statistical uncertainties\blue{, while t}he total error bars denote the statistical and systematic uncertainties added in quadrature. The \blue{simulated fractional} contribution \blue{from associated production} to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bca_0607}
\end{center}
 \end{figure}

@@

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}. The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest value of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude has no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must diminish at \blue{small} $-t$ values due to the dependence of the amplitude on the factor $k$ from in Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The twist-3 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitudes are compatible with zero, as are the twist-3 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitudes\blue{, which are} dependent on the squared DVCS term. These \blue{$A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitudes} are shown in the second row of Fig.~\ref{bsa_xbjrange}. Neither the \blue{$A_{\textrm{LU,DVCS}}^{\sin\phi}$ nor the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitudes} show any clear dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$. The systematic error bands of the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used \blue{used in the various stages} of the H{\sc ermes} experiment.

@@

The curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data~\cite{Kum09}. The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewedness and $t$ dependences. In the model, the $t$ dependence is approximated by a physically-motivated Regge dependence. The solid curves represent the model \blue{fit} without data from experiment\blue{s} \cite{Cam06, Gir08} at Hall A in Jefferson Laboratory; the model \blue{fit} represented by the dashed curves \blue{includes} this data. Both fits include the 1996-2005 H{\sc ermes} data. The model incorporates only twist-2 GPDs and so can provide calculations only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is well described by the model. \blue{Both the $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes favour the GPD fit that did not include the Hall A data.}

The asymmetry amplitudes shown in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} were also re-binned as a function of $-t$ for three different ranges of $x_{\textrm{B}}$. There was no observed dependence of any of the amplitudes with this two dimensional binning.
